\pdftitle

### 2017-05-12 maxNt.tex
add to intro

%% Author: PGL  Porta Mana
%% Created: 2015-11-04T09:20:08+0100
%% Last-Updated: 2017-05-12T13:15:15+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Report-no: ***
\documentclass{article}

@@

Maximum-entropy models are used for a variety of reasons, sometimes not
completely clear. For our purposes we can simply say that the \me\ method
is assumed to generate a \enquote{maximally noncommital} \cite{jaynes1963}
probability distribution. We intend the quoted expression only as an
umbrella term, also because it  means very little without further
clarifications.

The neurons recorded in these kinds of experiments are not usually
specifically chosen, and from their observation we expect to learn
something about all other neurons in the same brain area. That is, they are
assumed to be a \enquote{representative random sample} of the neurons in
that area. Our discussion hinges on this often just tacitly understood
assumption.

@@

>>>>

%% Author: PGL  Porta Mana
%% Created: 2015-11-04T09:20:08+0100
%% Last-Updated: 2017-05-12T13:32:47+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Report-no: ***
\documentclass{article}

@@

Maximum-entropy models are used for a variety of reasons; sometimes not
completely clear ones. For our purposes we can simply say that the \me\
method is assumed to generate a \enquote{maximally noncommital}
\cite{jaynes1963} probability distribution. We intend the quoted expression
only as an umbrella term, also because it means very little without further
clarifications.

The neurons recorded in these kinds of experiments are usually not
specifically chosen, and from their observation we expect to learn
something about all other neurons in the same brain area. That is, they are
assumed to be a \enquote{representative random sample} of the neurons in
that area. Our discussion hinges on this often just tacitly understood
assumption.

@@

In other words, if our sample is \enquote{random} and
\enquote{representative} of some population, then we must choose which of
them has a \enquote{maximally noncommittal} distribution: the sample or the
population. We can't choose both. Which choice is most meaningful? It goes
without saying that if either is \enquote{maximally noncommittal}, the
other must be somehow \enquote{committal}.

***
